\subsection{Technical Requirements}
\subsubsection{Functional Requirements}
The PRT data collection project has functional requirements that include PRT location tracking, power usage, and vehicle occupancy. 
Other requirements include displaying data in a single-page user interface, calculating time to complete a ride as well as various accompanying statistics, and supplying data to PRT officials to increase the efficiency of the PRT system.
\begin{enumerate}
    \item Analyze location and power data.
    \item Display data in a single-page user interface.
    \item Track vehicle occupancy
    \item Track vehicle location and time to complete a ride
    \item Supply data to PRT officials to increase the efficiency of the PRT system
\end{enumerate}
\subsubsection{Engineering Requirements}
In order to gather data about the PRT cars, it is necessary to equip the PRT cars with a Raspberry Pi 4 Model B as well as additional sensors such as a current clamp and LiDAR to track occupancy. 
The devices should be non-visible to ensure they are not targeted by passengers and transmit the data wirelessly while at the platforms. 
The transmission will be encrypted to prevent session hijacking and will be immediately stored in an SQL database. 
The data collected will then be used to make predictions to better improve the PRT.
\begin{enumerate}
    \item Equip PRT cars with a Raspberry Pi 4 Model B.
    \item Attach additional sensors (GPS, Current Clamp).
    \item Devices should be non-visible to the occupants.
    \item Data will be transmitted to the database while at PRT platforms.
    \item Data will be transmitted wirelessly.
    \item Data transmitted with be encrypted.
    \item Data will be stored in a SQL database.
    \item The database will be kept securely to ensure the confidentiality of data.
    \item Use of Infrared or LiDAR to determine vehicle occupancy.
    \item Use data collected to make predictions
\end{enumerate}

\subsection{Broader Constraints}
\input{sections/design requirements and constraints/broader constraints.tex}